Appendix 4: Species distribution model comparison between INLA and sdmTMB

### 2022-01-05 doc/appendix-binomial-inla.Rmd
Fix inlabru prediction

Or, we can make the prediction with inlabru:

```{r inla-pred, out.width="6in"}
nd_bru <- nd
nd_bru <- dplyr::left_join(nd_bru, yr_lu)
sp::coordinates(nd_bru) <- c("X", "Y")
nd_bru <- as(nd_bru, "SpatialPixelsDataFrame")
pred_bru <- predict(m_bru, data = nd_bru)

nrow(pred_bru$Predictor)
```

>>>>

Or, we can make the prediction with inlabru. To do that, we must recreate `i_year`, create a `SpatialPixelsDataFrame` class data frame, and specify in `formula` to include both the random field (`f`), the factors (`fac`), and use the inverse-link transformation `plogis()`:

```{r inlabru-pred, out.width="6in"}
nd_bru <- nd
nd_bru <- dplyr::left_join(nd_bru, yr_lu)
sp::coordinates(nd_bru) <- c("X", "Y")
nd_bru <- as(nd_bru, "SpatialPixelsDataFrame")
pred_bru <- predict(m_bru, data = nd_bru, formula = ~ plogis(f + fac))
ggplot(as.data.frame(pred_bru)) +
  geom_raster(aes(X, Y, fill = mean)) +
  facet_wrap(~year) +
  scale_fill_viridis_c() +
  coord_fixed()
```
